The effects of priming in human computation

### 2014-05-11 docs/draft/pnas2.tex
changes to manuscript and specificity computation

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun and remuneration.  A typical task might be the 
flagging of innapropriate images, something that people are still better at 
than computers.

Such platforms render human cognition as fluid a resource as compute cycles: 
it is available on demand in small units, with low transaction cost, from 
anywhere 
via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.  The 
result is that one can treat AMT like a compute cluster, and seemlessly 
integrate human and machine intelligence in large-scale computations.

This development invites a new perspective on the role of human cognition 
in technical systems.  Researchers have put forward the term HPU 
(Human co-Processing Unit)\footnote{We acknowledge the irony of this term:
the original meaning of `computer' was a person who performs computations,
its reference to machines being a personification brought into usage in the 
late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.  Thinking of networked 
people as compute systems is not new.  Working in operations research, Simon 
and Newell viewed the primary activity of human organizations to be 
computation\cite{Simon:1958fp}.

In adopting this view, we must contend with a stark difference between 
people and CPUs: even when given the same instructions, people do not produce
the same output.  In other words, one pays for the ``high level instructions 
set'' of HPUs by accepting variability in outputs.

Variability raises a quality control issue \cite{kazai2013analysis}. There 
have been many studies 
into how user interface design, payments, social reputation schemes, and the 
disclosure of the wider purpose of tasks affect worker outputs. We will 
review the prior work in the section following this one.
{\em Here, we report our investigation of worker {\em hysteresis}, that is, 
the tendency of a worker's output during one task to be influenced by other 
recently completed tasks}.

We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones 
(see \textbf{Fig. A}), and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are, and how often workers make 
cultural references.

Our primary interest lays in the hysteretic effects of in-task priming.  We
include framing mainly as a point of comparison.  A defensible expectation is
that the framing would produce a much stronger effect, because it clearly 
signals the requester's interest in a specific aspect of image content. 
Remarkably, with respect to the specificity of labels, and their content 
(either food- or culture-orineted), in-task priming produces much stronger 
effects.

However, to measure the effects of priming, one generally has to make an 
assumption about what those effects will be.  At risk of circularity, the 
definition of priming itself is traditionally operationalized in terms 
of these effects \cite{}.  We seek to alleviate this 
situation by providing an application-independant definition of priming 
suitable for studying HPUs hysteresis.  We 
present this definition following the section on prior work.

\subsection*{Prior Work}

The notion of human computation in its modern form is attributed to von Ahn 
and L Dabbish for their demonstration of the \textit{ESP Game}, a system 
through which people label images by trying to guess the labels given by 
others \cite{von2004labeling}.  In this form, and on platforms like AMT,
is a kind of Crowdsourcing.

In crowdsourcing, an open call to is made an unstructured pool of workers 
\cite{howe2008crowdsourcing}.  There is generally no long-term engagement 
between worker and employer, and the ability 
to screen workers (say, for expertise) is usually very limited 
\cite{howe2008crowdsourcing}.  This raises its own quality issue 
\cite{lease2011quality}, distinct from the effects of hysteresis.

Reports on the reliability of crowdsourced output using AMT vary from very
bad \cite{marsden2009crowdsourcing} to quite good 
\cite{alonso2009can, grady2010crowdsourcing}. Kazai et al find that 
crowdsourced workers vary
greatly in their levels of attentiveness and accuracy, and that this 
variability in part depends on how interesting they find the task, whether they
judge
themselves to have expertise in the task domain, and whether they feel they
are being paid enough \cite{kazai2013analysis}.  Interestingly, workers that
indicated having expertise in the task were less likely to find it interesting,
spent less time on the task, and did more poorly.

Generally, some portion of responses appear to be random probably because
the worker is not bothering to actually perform the work as intended
\cite{lease2011quality}(check).  By including honeypots (traps that workers who are
catch workers who are not paying attention) such cheating can be screened out 
to some degree \cite{snow2008cheap}, as can filtering out repsonses
that have a very short completion time \cite{kazai2013analysis}.

The above methods could be considered post-processing, but pre-screening 
workers can be done as well. AMT provides the requester the ability to screen
workers based on their history of accepted task completions. But Paolacci et al
report good success in screening workers other attributes, even cultural ones
\cite{paolacci2010running}.  Training workers is another straightforward way 
to improve overall worker profficiency \cite{le2010ensuring}.

Other researchers have investigated how motivation, context, framing, and 
social factors affect worker performance.  Kazai et al found that workers 
motivated by payment were more accurate \cite{kazai2013analysis}, especially
if payment was neither too high nor too low.
A carefully designed user interface also improves worker performance 
\cite{Finnerty2013} as does telling the worker the wider workflow context that
of which their task is a part \cite{Kinnaird2012281}. Chandler and Kapelner
studied the effect of telling workers that their results would be used for
medical research, and found that workers were more likely to participate, but
did not provide more accurate work than when told nothing 
\cite{chandler2013breaking}.

Despite the wealth of research investigating the factors influencing 
performance in crowdsourcing, we are unable to find any work showing the 
effects of in-task priming as we have described it.  This is concerning 
because, in the psychology literature, it is well known that priming can have 
powerful effects for perceptual tasks related to visual 
recognition of objects \cite{BJOP:BJOP1796}, auditory recognition of words 
\cite{BJOP:BJOP1826}, and the recognition
of gender* and affect*.  These are, of course, precisely the types of tasks 
for which AMT is used \cite{yuen2011survey, snow2008cheap}.

In psychology, priming is a phenomenon whereby previous exposure to a 
stimulus leads to faster, or more accurate responses to similar stimuli 
\cite{Ghuman17062008}, or to lower response thresholds \cite{BJOP:BJOP1826}.
Priming works through various mechanisms.

One mechanism appears to be 
closely related to stimulus encoding \cite{BJOP:BJOP1826}.
Participants are better able to recognize a word in a noisy background when 
primed with a word that shares morphemes 
(e.g. ``reflects'' and ``reflecting'').  However, priming 
with a word that is semantically related, but does not share morphemes doesn't 
help (e.g. ``held'' and ``holding'')\cite{BJOP:BJOP1826}.  Other studies seem
to provide definitive evidence that priming leads to better 
application of object knowledge and top-down processes \cite{Ghuman17062008},
and can also act to facilitate memory access \cite{beller1971priming}.

But the the underlying mechanisms in priming
can be exceedingly subtle \cite{BJOP:BJOP1796}.  As one expects exposing 
participants to an image hels them subsequently recognise that 
image when seen in a tachistoscope.  The researches demonstrated that priming 
using an image that was visually different but of an object having the same 
name also helped participants subsequently identify the image in the 
tachistoscope.  Surprisingly, being presented with related word and 
reading it aloud did not help.  On the basis of these 
results, the researchers suggest the existence of a visual-semantic system,
distinct from the linguistic one \cite{BJOP:BJOP1796}.

Based on the compelling evidence for priming effects in task types often 
employed on AMT, we hypothesize that workers' performance may be impacted
by the very work they have recently performed.  However, we adapt the 
operationalization of priming from one based on speed, accuracy, and 
response threshold, to an algorithmic definition that makes no particular
assumptions about the nature of priming effects.

\section*{Text}
\subsection*{An algorithmic definition of priming}
One difficulty with the notion of priming is that there appears to be no 
defensible notion of an ``unprimed state''.  Consider the ambiguous image set 
in our experiment.  Would we be better to include a treatment with no
priming images at all?  We argue that, in that case, one would mainly observe  
effects of \textit{primacy}.  
Further, a participant always enters the experiment in \textit{some} state of 
mind, depending on her exposures prior to the experiment, which cannot be 
known by the experimenter.  By including a priming exposure that is in some 
sense `neutral' for the purposes of an experiment, one at least makes the 
priming of participants more uniform.

@@

\subsection*{Results}
\paragraph{All treatments were differently primed.}
We test for priming effects using our definition proposed in the introduction,
implemented with a Naive Bayes classifier.  \textbf{Figure 1} shows
the classifier performance in distinguishing between different pairs of 
treatments, when provided workers' labels for the test images.

The classifier distinguishes the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(in-task and framing) were effective.  It is perhaps not surprising that
a Naive Bayes classifier can distinguish treatments tending toward a different 
``orientation'', e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$
(\textbf{Fig. 1A}).
But it is remarkable that, based only on the labels provided for the five test 
images, the classifier can distinguish workers from treatments of the 
\textit{same} orientation, such as $\textsc{cult}_{img}$ and 
$\textsc{cult}_{fund, img}$, with high accuracy (\textbf{Fig. 1B}).

Next we look at the degree to which labels from individual test images reveal 
priming.  It would stand to reason that, as workers proceed through 
the test images, the effects of priming might be ``washed out''.  
\textbf{Figure 2} shows the
performance of the Naive Bayes classifier when using the labels workers provide
for particular images.  This does show that, as we look to later test images, 
the treatments' difference in priming, $\theta_\text{NB}$, declines.

@@

\textbf{Figure 3} plots the composition of labels (fraction of culture- and 
food-oriented labels) for different treatments and images.  In 
panel \textbf{A}, we can see that, before considering the effects of 
treatments, there is significant variance in the composition of the labels 
for different images due to inherent differences in their content.  For our 
purpose, we are interested in the differential of composition between 
different treatments.

In \textbf{Fig. 3B} we exhibit the composition of labels for the various 
treatments (aggregating together the labels for all images for a given 
treatment).  We can see that the treatments which expose workers to the
cultural image sets do elicit significantly more culture-oriented and fewer
food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
also apperas that all the $\textsc{ingr}_x$ treatments produce more 
food-oriented labels, but we cannot assert this at significance 
$\alpha = 0.05$.

The effect size, however, is somewhat small.  Since we observed that priming 
difference ``wears off'', it may be the case 
that aggregating label compositions for all images actually masks the effects. 
In \textbf{Fig. 3C}, we plot label compositions for only the first
image.  This reveals that, in labeling the first test image, workers in the
$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
food-oriented labels.  The effect was strong enough to essentially reverse 
the proportions of these labels compared to the other treatments.

We next inspect this effect longitudinally, that is, as a function of 
the test image.  To do so, we compute the ``excess cultural orientation'' 
($\Delta_{cult}$) of
the $\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment (2500).  
Intuitively, this is intended to capture how much 
more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
\textbf{Figure 4} plots $\Delta_{cult}$ as a function of test image, $i$. It
clearly shows the strong influence on the labels attributed to the first image,
but this effect immediately drops below statistically measureable levels, while
remaining always positive.

@@

We can compare the bulk specificity of two treatments by taking a subsample
of workers from each, and the labels of the workers in one
subsample to each of those in the other.  In drawing this comparison, we only 
compare labels that were attributed to the same image.  Thus the relative 
specificity of two treatments can then be computed as:
\begin{align}
	S(\textsc{x},\textsc{y}) = 
		\sum_{i=1}^5 \; 
		\sum_{\ell\in \mathcal{L}(\textsc{x},i)} \;
		\sum_{m\in \mathcal{L}
		(\textsc{y},i)} \left(\mathbf{1}[\ell > m] 
		- \mathbf{1}[m>\ell]\right),
\end{align}
Where \textsc{x} and \textsc{y} are treatment subsamples,
$\mathcal{L}(\textsc{x},i)$ is the set of all labels produced by workers in 
$\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 5} 
exhibits the results.

@@

\paragraph{The rate of priming wash-out depends on how it is measured}
Seeing that $\theta_\text{NB}$ declines as one proceeds through the test 
images (\textbf{Fig. 2}), one should ask whether this actually represents 
priming wash-out.  One might also attribute this to 
differences in the \textit{content} of the images.  Nevertheless, we can
certainly assert that the effects of priming detected by the classifier 
persisted through the labelling of all five test images.

It is interesting to compare this to the result in \textbf{Fig. 4}, which
shows that the effect of priming on \textit{orientation} (culture vs food) 
decays much more quickly than the overall effects detected by
the classifier.  We take this to be the result of the complex network of 
mechanisms likely to be at play in priming, wherein the orientation of focus
is one mechanism that is particularly fast-responding.

@@

Even with the above explanations, is surprising that 
$\textsc{cult}_{img,x}$ simultaneously could be strongly influenced to 
produce a higher quantity of culture-oriented labels, and yet not a higher
specificity of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first test image 
(see \textbf{Fig. 4}), we also
performed the specificity analysis restricting to labels from the first
test image (see \textbf{Fig. S1}).  But even focusing on the first test image
shows no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that orientation of focus and 
label specificity do not necessarily.

@@

\paragraph{Figure 1.}
$F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa.

\paragraph{Figure 2.}
$F_1$ score and $\theta_\text{NB}$ for the classification of 
$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
classifier.  The classifier is provided only the labels attributed to
particular images as indicated on the abscissa.

\paragraph{Figure 3.}
Percent label composition (culture- vs food-oriented labels) for 
various images and treatments.  Panel A shows the composition of 
labels, aggregated over all treatments, as a function of test image.
Panel B shows the composition of labels, aggregated over all images, as
a function of treatment.  Panel C shows the composition of labels 
attributed to the first test image by various treatments.

\paragraph{Figure 4.}
Excess culture-oriented label composition in the labels provided
by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
test images (see \textbf{Eq. 1} for calculation).

\paragraph{Figure 5.}
Relative specificity of various treatments.
Each panel shows the comparison between a basis treatment (inset) and 
target treatments (abscissa).
Bar heights indicate relative specificity of the target 
treatment compared to the basis (a positive quantity means the target 
is more specific), and are normalized to units of standard 
deviations of the null comparison.  Dotted horizontal lines indicate
the 95\% confidence interval for the null comparison, which necessarily
has zero relative specificity (see \textbf{Methods} 
for an explanation of the null comparison).  Panels D, E, and F 
represent relative specificity calculated using only culture-oriented
labels, while panels G, H, and I using only food-oriented labels.
Labels that are both culture- and food-oriented are excluded from the
calculations for panels D through I.

>>>>

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun and remuneration.  Tasks involving qualitative
judgment (e.g. flagging innapropriate images), natural language annotation,
and object recognition are commonplace, since people still outperform  
computers in these areas.

Such platforms render human cognition as fluid a resource as compute cycles: 
it is available on demand in small units, with low transaction cost, from 
anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
The task requestor can interact with the platform like a compute server, 
seemlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
term: the original meaning of `computer' was a person who performs 
computations, its reference to machines being a personification brought into 
usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.

Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and provide qualitative annotations of datasets in a research 
setting.  Given the limited ability to screen workers, and their transient 
low-commitment engagement with the employer, researchers have criticised the
reliability of crowdsourced output \cite{marsden2009crowdsourcing}.

For 
example, cheating
is a problem \cite{lease2011quality}, but straightforward methods have been 
developped to screen out cheaters \cite{snow2008cheap, kazai2013analysis}.
Still, there is a great deal of variance in worker attention and 
accuracy \cite{kazai2013analysis}.  Researchers have found many factors that 
modulate worker performance, such as level of pay\cite{kazai2013analysis}, 
training\cite{le2010ensuring}, pre-screening 
workers\cite{paolacci2010running},  user-interface design
\cite{Finnerty2013}, providing context for the task in the wider workflow
\cite{Kinnaird2012281}, and disclosing the purpose of the task 
\cite{chandler2013breaking}.

Here we are concerned with effects of a more subtle origin: the influence that
prior tasks have on subsequent ones.  Psychology experiments document the 
strong effects that a prior exposure to stimulus can have on participants' 
performance in related tasks, a phenomenon known as \textit{priming}.  Strong 
priming effects have been demonstrated for
perceptual tasks such as the visual recognition of 
objects \cite{BJOP:BJOP1796},
auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
of gender* and affect*: precisely the kinds of tasks well-served by microtask 
platforms \cite{yuen2011survey, snow2008cheap}.

Reserearchers 
have investigated various effects due to \textit{framing}, at the outset of 
the task.  But psychological experiments show that priming is strongest when 
delivered through the same modality as the task.  This suggests that it might
be more important to investigate the effects of priming that occurs 
\textit{during} tasks.  We call such effects \textit{in-task priming}.  
Whereas requestors can take measures to frame 
their task as they see fit, in-task priming would be unavoidable in many 
contexts, with consequences for the validity of microtask platforms as a 
research tool.

We investigate the effects of in-task priming on using an image-labeling task
on the AMT platform.  Each worker is required to label a \textit{prior set} of
images followed by a \textit{posterior set}, but no distinction is made between
these sets from the perspective of the worker.  The posterior set is
always the same, but workers are randomly assigned one of three prior sets.
We analyze effects on the labels given to the the posterior set in terms of 
what aspects the workers focus on (``orientation of labels''), and the degree 
of specificity of the labels, both of direct consequence to the quality of 
labeling and classification.

As a point of comparison, we subject some groups of workers to a kind of
framing, by disclosing a semantically-loaded (fictitious) name of the 
funder of the research.  Remarkably, we find that in-task priming has a much 
stronger effect
on label orientation and specificity.  This has major implications for the 
design of qualitative labeling and classification tasks.  Our results show that
significant bias in worker labelling can be introduced by the progression of 
tasks.  On the other hand, our results suggest the progression of tasks can 
alse be used to tune workers to produce more nuanced output.

Traditionally, priming effects are
measured using methods chosen to elucidate the underlying psychological 
mechanisms.  For the human computation context, we seek general 
methods that detect any hysteresis effects in HPUs, whatever they may be.  
Here we present a novel general-purpose method for detecting priming, based on 
a rigorous algorithmic definition. 
This method provides a powerful new tool for detecting priming in populations
without having to know anything about how the priming was carried out, nor the 
effects that it might be expected to have.
We demonstrate the utility of this method by showing that
it can detect priming effects of all treatments in our experiment, even when 
they fail to be detected through their effects on label orientation and 
specificity. This method has the potential for a wide range of applications 
outside computer science.

\section*{Text}
\subsection*{An algorithmic definition of priming}
Motivate the need for this kind of instrumentalization.

One difficulty with the notion of priming is that there appears to be no 
defensible notion of an ``unprimed state''.  Consider the ambiguous image set 
in our experiment.  Would we be better to include a treatment with no
priming images at all?  We argue that, in that case, one would mainly observe  
effects of \textit{primacy}.  
Further, a participant always enters the experiment in \textit{some} state of 
mind, depending on her exposures prior to the experiment, which cannot be 
known by the experimenter.  By including a priming exposure that is in some 
sense `neutral' for the purposes of an experiment, one at least makes the 
priming of participants more uniform.

@@

\subsection{Experimental Setup}
We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones 
(see \textbf{Fig. A}), and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are, and how often workers make 
cultural references.

\subsection*{Results}
\paragraph{All treatments were differently primed.}
We test for priming effects using our definition proposed in the introduction,
implemented with a Naive Bayes classifier.  \textbf{Figure 5} shows
the classifier performance in distinguishing between different pairs of 
treatments, when provided workers' labels for the test images.

The classifier distinguishes the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(in-task and framing) were effective.  It is perhaps not surprising that
a Naive Bayes classifier can distinguish treatments tending toward a different 
``orientation'', e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$
(\textbf{Fig. 5A}).
But it is remarkable that, based only on the labels provided for the five test 
images, the classifier can distinguish workers from treatments of the 
\textit{same} orientation, such as $\textsc{cult}_{img}$ and 
$\textsc{cult}_{fund, img}$, with high accuracy (\textbf{Fig. 5B}).

Next we look at the degree to which labels from individual test images reveal 
priming.  It would stand to reason that, as workers proceed through 
the test images, the effects of priming might be ``washed out''.  
\textbf{Figure 6} shows the
performance of the Naive Bayes classifier when using the labels workers provide
for particular images.  This does show that, as we look to later test images, 
the treatments' difference in priming, $\theta_\text{NB}$, declines.

@@

\textbf{Figure 7} plots the composition of labels (fraction of culture- and 
food-oriented labels) for different treatments and images.  In 
panel \textbf{A}, we can see that, before considering the effects of 
treatments, there is significant variance in the composition of the labels 
for different images due to inherent differences in their content.  For our 
purpose, we are interested in the differential of composition between 
different treatments.

In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
treatments (aggregating together the labels for all images for a given 
treatment).  We can see that the treatments which expose workers to the
cultural image sets do elicit significantly more culture-oriented and fewer
food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
also apperas that all the $\textsc{ingr}_x$ treatments produce more 
food-oriented labels, but we cannot assert this at significance 
$\alpha = 0.05$.

The effect size, however, is somewhat small.  Since we observed that priming 
difference ``wears off'', it may be the case 
that aggregating label compositions for all images actually masks the effects. 
In \textbf{Fig. 7C}, we plot label compositions for only the first
image.  This reveals that, in labeling the first test image, workers in the
$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
food-oriented labels.  The effect was strong enough to essentially reverse 
the proportions of these labels compared to the other treatments.

We next inspect this effect longitudinally, that is, as a function of 
the test image.  To do so, we compute the ``excess cultural orientation'' 
($\Delta_{cult}$) of
the $\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment (2500).  
Intuitively, this is intended to capture how much 
more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
\textbf{Figure 8} plots $\Delta_{cult}$ as a function of test image, $i$. It
clearly shows the strong influence on the labels attributed to the first image,
but this effect immediately drops below statistically measureable levels, while
remaining always positive.

@@

We can compare the bulk specificity of two treatments by taking a subsample
of workers from each, and the labels of the workers in one
subsample to each of those in the other.  In drawing this comparison, we only 
compare labels that were attributed to the same image.  Thus the relative 
specificity of two treatments can then be computed as:
\begin{align}
	S(\textsc{x},\textsc{y}) = 
		\sum_{i=1}^5 \; 
		\sum_{\ell\in \mathcal{L}(\textsc{x},i)} \;
		\sum_{m\in \mathcal{L}
		(\textsc{y},i)} \left(\mathbf{1}[\ell > m] 
		- \mathbf{1}[m>\ell]\right),
\end{align}
Where \textsc{x} and \textsc{y} are treatment subsamples,
$\mathcal{L}(\textsc{x},i)$ is the set of all labels produced by workers in 
$\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 9} 
exhibits the results.

@@

\paragraph{The rate of priming wash-out depends on how it is measured}
Seeing that $\theta_\text{NB}$ declines as one proceeds through the test 
images (\textbf{Fig. 6}), one should ask whether this actually represents 
priming wash-out.  One might also attribute this to 
differences in the \textit{content} of the images.  Nevertheless, we can
certainly assert that the effects of priming detected by the classifier 
persisted through the labelling of all five test images.

It is interesting to compare this to the result in \textbf{Fig. 8}, which
shows that the effect of priming on \textit{orientation} (culture vs food) 
decays much more quickly than the overall effects detected by
the classifier.  We take this to be the result of the complex network of 
mechanisms likely to be at play in priming, wherein the orientation of focus
is one mechanism that is particularly fast-responding.

@@

Even with the above explanations, is surprising that 
$\textsc{cult}_{img,x}$ simultaneously could be strongly influenced to 
produce a higher quantity of culture-oriented labels, and yet not a higher
specificity of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first test image 
(see \textbf{Fig. 8}), we also
performed the specificity analysis restricting to labels from the first
test image (see \textbf{Fig. S1}).  But even focusing on the first test image
shows no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that orientation of focus and 
label specificity do not necessarily.

@@

\paragraph{Figure 5.}
$F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa.

\paragraph{Figure 6.}
$F_1$ score and $\theta_\text{NB}$ for the classification of 
$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
classifier.  The classifier is provided only the labels attributed to
particular images as indicated on the abscissa.

\paragraph{Figure 7.}
Percent label composition (culture- vs food-oriented labels) for 
various images and treatments.  Panel A shows the composition of 
labels, aggregated over all treatments, as a function of test image.
Panel B shows the composition of labels, aggregated over all images, as
a function of treatment.  Panel C shows the composition of labels 
attributed to the first test image by various treatments.

\paragraph{Figure 8.}
Excess culture-oriented label composition in the labels provided
by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
test images (see \textbf{Eq. 1} for calculation).

\paragraph{Figure 9.}
Relative specificity of various treatments.
Each panel shows the comparison between a basis treatment (inset) and 
target treatments (abscissa).
Bar heights indicate relative specificity of the target 
treatment compared to the basis (a positive quantity means the target 
is more specific), and are normalized to units of standard 
deviations of the null comparison.  Dotted horizontal lines indicate
the 95\% confidence interval for the null comparison, which necessarily
has zero relative specificity (see \textbf{Methods} 
for an explanation of the null comparison).  Panels D, E, and F 
represent relative specificity calculated using only culture-oriented
labels, while panels G, H, and I using only food-oriented labels.
Labels that are both culture- and food-oriented are excluded from the
calculations for panels D through I.
